---
title: "Fertilice Right"
title-block-banner: true
date: today
number-sections: true
format:
   html:
    toc: true
    toc-location: left
    toc-expand: 3
    number-sections: true
    number-depth: 3
    theme: cosmo
    df-print: paged
    code-fold: true 
    output-fold: true
editor: visual
---

<!-- Zoom for figures -->

```{css zoom-lib-src, echo = FALSE}
script src = "https://ajax.googleapis.com/ajax/libs/jquery/3.4.1/jquery.min.js"
```

```{js zoom-jquery, echo = FALSE}
 $(document).ready(function() {
    $('body').prepend('<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>');
    // onClick function for all plots (img's)
    $('img:not(.zoomImg)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src')).css({width: '100%'});
      $('.zoomDiv').css({opacity: '1', width: 'auto', border: '1px solid white', borderRadius: '5px', position: 'fixed', top: '50%', left: '50%', marginRight: '-50%', transform: 'translate(-50%, -50%)', boxShadow: '0px 0px 50px #888888', zIndex: '50', overflow: 'auto', maxHeight: '100%'});
    });
    // onClick function for zoomImg
    $('img.zoomImg').click(function() {
      $('.zoomDiv').css({opacity: '0', width: '0%'}); 
    });
  });
```

First, we will organize the information in our data frame according to the accumulated recommendations for each treatment to observe differences between them. We will focus on the recommendations for each **crop (Rice and Banana)**.

-   Organize our dataset according to the following recommendations:
    -   Accumulated recommendations for each treatment.
    -   Different treatments for each crop, focusing on the principal elements **(N, P, and K)**, recommendations along all farms.
    -   Establish differences between the elements applications.

Through this we will be able to answer the followed questions:

-   How do the different treatments affect the nutrient recommendations for each crop?
-   What are the differences between the nutrient recommendations for each crop?
-   Are we reaching the objectives of the fertilization plan?

let's start by loading the necessary libraries and the data frame.

```{r}
#| echo: true
#| output: false
#| warning: false
#| message: false

# Load the necessary libraries

list_p <- c("tidyverse", "readxl", "soiltexture", 
            "readr", "caret", "plotly")

sapply(list_p, function(x) {
       if(!require(x, character.only = TRUE)) {
         install.packages(x, dependencies = TRUE)
         library(x, character.only = TRUE)
       }
       })

FR_Plan <- read_excel("D:\\OneDrive - CGIAR\\Fertilize Right ADMIN\\ACTIVIDADES\\A3. LB Suelos\\Analisis/Fertilizacion.xlsx", 
                    na = c("null", NA), sheet = "Fertilizations") ## Fertilization plan for both crops
FR_SL <- read_excel("D:\\OneDrive - CGIAR\\Fertilize Right ADMIN\\ACTIVIDADES\\A3. LB Suelos\\Analisis\\Suelos_LB.xlsx",
                    na = c("null", NA)) ## Soil data analysis results for both crops


str(FR_Plan)
summary(FR_Plan)
```

Once we have our data uploaded, let's select the variables that we will implement for our analysis. In this case, we will focus on the **Treatment, Crop, and the Nutrient recommendations (N, P, and K)**.

Lets select the data that we will use for our analysis.

```{r}

```


::: {.panel-tabset .nav-pills}
## Rice

```{r}
#| echo: true
#| output: true
#| message: false
#| warning: false

# Observe the difference between N, P, and K applications for the rice crop.

FR_Plan |>
  filter(Cultivo == "Arroz") |>
  group_by(Finca, Tratamiento) |>
  mutate(N_kg_ha = mean(`Aporte N (Kg/ha)`, na.rm = TRUE),
         P_kg_ha = mean(`Aporte P (Kg/ha)`, na.rm = TRUE),
         K_kg_ha = mean(`Aporte K (Kg/ha)`, na.rm = TRUE), 
         Tratamiento = factor(Tratamiento, 
                              levels = c("Convencional", "Optimizado", "Alternativo"))) |>
  pivot_longer(cols = c(N_kg_ha, P_kg_ha, K_kg_ha),
               names_to = "Variables", values_to = "Values") |>
  ggplot(aes(x = Finca, y = Values, 
             fill = Tratamiento)) +
  geom_col(position = "dodge", width =  0.5) +
  facet_wrap(~ Variables, scales = "free_y") +
  scale_fill_manual(values = c("#F4A460", "#48D1CC", "#B0E0E6")) +
  guides(color = "none") +
  theme_light(base_size = 12) +
  theme(axis.title.x = element_text(size = 8, face = "bold.italic"),
        axis.title.y = element_text(size = 8, face = "bold.italic"),
        legend.title = element_text(size = 8, face = "bold"),
        axis.text.x = element_text(size = 6, face = "bold"),
        strip.text = element_text(size = 8, face = "bold"))
  

```

## Banana

```{r}
#| echo: true
#| output: true
#| message: false
#| warning: false

# Plotting the data

FR_Plan |>
  filter(Cultivo == "Banano") |>
  group_by(Finca, Tratamiento) |>
  mutate(N_kg_ha = mean(`Aporte N (Kg/ha)`, na.rm = TRUE),
         P_kg_ha = mean(`Aporte P (Kg/ha)`, na.rm = TRUE),
         K_kg_ha = mean(`Aporte K (Kg/ha)`, na.rm = TRUE), 
         Tratamiento = factor(Tratamiento, 
                              levels = c("Convencional", "Optimizado", "Alternativo"))) |>
  pivot_longer(cols = c(N_kg_ha, P_kg_ha, K_kg_ha),
               names_to = "Variables", values_to = "Values") |>
  ggplot(aes(x = Variables, y = Values, 
             fill = Tratamiento)) +
  geom_col(position = "dodge", width =  0.5) +
  facet_wrap(~ Variables, scales = "free_y") +
  scale_fill_manual(values = c("#F4A460", "#48D1CC", "#B0E0E6")) +
  guides(color = "none") +
  theme_light(base_size = 12) +
  theme(axis.title.x = element_text(size = 8, face = "bold.italic"),
        axis.title.y = element_text(size = 8, face = "bold.italic"),
        legend.title = element_text(size = 8, face = "bold"),
        axis.text.x = element_text(size = 6, face = "bold"),
        strip.text = element_text(size = 8, face = "bold"))

```
:::

Let's make an acummulative plot considering the nitrogen, phosphorus, and potassium applications for the rice crop.

::: {.panel-tabset .nav-pills}
## Rice

```{r}
#| echo: true
#| output: true
#| message: false
#| warning: false

FR_Plan |> 
  filter(Cultivo == "Arroz") |>
  mutate(DDS = as.numeric(DDS)) |>
  arrange(Finca, Tratamiento, DDS) |>
  group_by(Finca, Tratamiento, DDS) |>
  summarize(Cum_N = sum(`Aporte N (Kg/ha)`, na.rm = TRUE),
            Cum_P = sum(`Aporte P (Kg/ha)`, na.rm = TRUE),
            Cum_K = sum(`Aporte K (Kg/ha)`, na.rm = TRUE)) |>
  mutate(Cum_N = cumsum(Cum_N),
         Cum_P = cumsum(Cum_P),
         Cum_K = cumsum(Cum_K)) |>
  pivot_longer(cols = c(Cum_N, Cum_P, Cum_K),
               names_to = "Variables", values_to = "Values") |>
  mutate(Variables = factor(Variables, levels = c("Cum_N", "Cum_P", "Cum_K"))) |>
  ggplot(aes(x = DDS, y = Values, colour = Tratamiento)) +
  geom_point(size = 2) +
  geom_smooth(method = "loess", se = FALSE, span = 1, size = 1.2, na.rm = TRUE) +
  facet_wrap(Finca ~ Variables, scales = "free_y") + 
    scale_color_manual(values = c("Convencional" = "#F4A460", 
                                "Optimizado" = "#48D1CC", 
                                "Alternativo" = "#B0E0E6")) +
  guides(color = guide_legend(title = "Tratamiento")) +
  guides(color = "none") +
  theme_light(base_size = 12) +
  theme(legend.position = "right",
        axis.title.x = element_text(size = 8, face = "bold.italic"),
        axis.title.y = element_text(size = 8, face = "bold.italic"),
        legend.title = element_text(size = 8, face = "bold"),
        axis.text.x = element_text(size = 6, face = "bold"),
        strip.text = element_text(size = 8, face = "bold"))

# Aggregate nutrient contribution by product
FR_Plan |>
  filter(Cultivo == "Arroz") |>
  group_by(Product) |>
  mutate(Total_N = sum(`Aporte N (Kg/ha)`, na.rm = TRUE),
            Total_P = sum(`Aporte P (Kg/ha)`, na.rm = TRUE),
            Total_K = sum(`Aporte K (Kg/ha)`, na.rm = TRUE)) |>
  pivot_longer(cols = c(Total_N, Total_P, Total_K),
               names_to = "Nutrient", values_to = "Value") |>
  mutate(Nutrient = factor(Nutrient, levels = c("Total_N", "Total_P", "Total_K"))) |> 
  ggplot(aes(x = reorder(Product, Value), y = Value, fill = Nutrient)) +
  geom_col(position = "dodge") +
  facet_wrap(Tratamiento ~ Finca, scales = "free_y") +
  coord_flip() +
  scale_fill_manual(values = c("#FF6A6A", "#EE9572", "#9BCD9B")) +
  labs(title = "Total Nutrient Contribution by Fertilizer Product",
       x = "Fertilizer Product", y = "Total Nutrient (Kg/ha)") +
  theme_minimal() + 
  theme(legend.position = "right",
        axis.title.x = element_text(size = 8, face = "bold.italic"),
        axis.title.y = element_text(size = 8, face = "bold.italic"),
        legend.title = element_text(size = 8, face = "bold"),
        axis.text.x = element_text(size = 6, face = "bold"),
        strip.text = element_text(size = 8, face = "bold"))



```

## Banana

```{r, warning=FALSE}
#| echo: true
#| output: true
#| message: false
#| warning: false

FR_Plan |> 
  filter(Cultivo == "Banano") |>
  mutate(DDS = as.numeric(DDS)) |>
  arrange(Finca, Tratamiento, DDS) |>
  group_by(Finca, Tratamiento, DDS) |>
  summarize(Cum_N = sum(`Aporte N (Kg/ha)`, na.rm = TRUE),
            Cum_P = sum(`Aporte P (Kg/ha)`, na.rm = TRUE),
            Cum_K = sum(`Aporte K (Kg/ha)`, na.rm = TRUE)) |>
  mutate(Cum_N = cumsum(Cum_N),
         Cum_P = cumsum(Cum_P),
         Cum_K = cumsum(Cum_K)) |>
  pivot_longer(cols = c(Cum_N, Cum_P, Cum_K),
               names_to = "Variables", values_to = "Values") |>
  mutate(Variables = factor(Variables, levels = c("Cum_N", "Cum_P", "Cum_K"))) |>
  ggplot(aes(x = DDS, y = Values, colour = Tratamiento)) +
  geom_point(size = 2) +
  geom_smooth(method = "loess", se = FALSE, span = 1, size = 1.2, na.rm = TRUE) +
  facet_wrap(Finca ~ Variables, scales = "free_y") + 
    scale_color_manual(values = c("Convencional" = "#F4A460", 
                                "Optimizado" = "#48D1CC", 
                                "Alternativo" = "#B0E0E6")) +
  guides(color = guide_legend(title = "Tratamiento")) +
  guides(color = "none") +
  theme_light(base_size = 12) +
  theme(legend.position = "right",
        axis.title.x = element_text(size = 8, face = "bold.italic"),
        axis.title.y = element_text(size = 8, face = "bold.italic"),
        legend.title = element_text(size = 8, face = "bold"),
        axis.text.x = element_text(size = 6, face = "bold"),
        strip.text = element_text(size = 8, face = "bold"))

# Aggregate nutrient contribution by product
FR_Plan |>
  filter(Cultivo == "Banano") |>
  group_by(Product) |>
  summarize(Total_N = sum(`Aporte N (Kg/ha)`, na.rm = TRUE),
            Total_P = sum(`Aporte P (Kg/ha)`, na.rm = TRUE),
            Total_K = sum(`Aporte K (Kg/ha)`, na.rm = TRUE)) |>
  pivot_longer(cols = c(Total_N, Total_P, Total_K),
               names_to = "Nutrient", values_to = "Value") |>
  mutate(Nutrient = factor(Nutrient, levels = c("Total_N", "Total_P", "Total_K"))) |> 
  ggplot(aes(x = reorder(Product, Value), y = Value, fill = Nutrient)) +
  geom_col(position = "dodge") +
  coord_flip() +
  scale_fill_manual(values = c("#FF6A6A", "#EE9572", "#9BCD9B")) +
  labs(title = "Total Nutrient Contribution by Fertilizer Product",
       x = "Fertilizer Product", y = "Total Nutrient (Kg/ha)") +
  theme_minimal() + 
  theme(legend.position = "right",
        axis.title.x = element_text(size = 8, face = "bold.italic"),
        axis.title.y = element_text(size = 8, face = "bold.italic"),
        legend.title = element_text(size = 8, face = "bold"),
        axis.text.x = element_text(size = 6, face = "bold"),
        strip.text = element_text(size = 8, face = "bold"))



```
:::

```{r}
#| echo: true
#| output: true
#| message: false
#| warning: false

# library(ggtern)  # Special package for ternary plots
# 
# # Prepare data for ternary plot
# FR_Plan |>
#   filter(!is.na(`Aporte N (Kg/ha)`), 
#          !is.na(`Aporte P (Kg/ha)`), 
#          !is.na(`Aporte K (Kg/ha)`)) |>
#   mutate(Total_NPK = `Aporte N (Kg/ha)` + `Aporte P (Kg/ha)` + `Aporte K (Kg/ha)`,
#          N_Ratio = `Aporte N (Kg/ha)` / Total_NPK,
#          P_Ratio = `Aporte P (Kg/ha)` / Total_NPK,
#          K_Ratio = `Aporte K (Kg/ha)` / Total_NPK) |>
#   ggtern(aes(x = N_Ratio, y = P_Ratio, z = K_Ratio, color = Tratamiento)) +
#   geom_point(size = 3) +
#   labs(title = "Ternary Plot of NPK Fertilization",
#        x = "Nitrogen Ratio", y = "Phosphorus Ratio", z = "Potassium Ratio") +
#   theme_minimal() +
#   scale_color_manual(values = c("Convencional" = "#F4A460", 
#                                 "Optimizado" = "#48D1CC", 
#                                 "Alternativo" = "#B0E0E6"))

```
