---
title: "Fertilice Right"
title-block-banner: true
date: today
number-sections: true
format:
   html:
    include-in-header:
      - text: |
          <script src = "https://ajax.googleapis.com/ajax/libs/jquery/3.4.1/jquery.min.js""></script>
          <script type="text/javascript">
            $(document).ready(function() {
              $('body').prepend('<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>');
              // onClick function for all plots (img's)
              $('img:not(.zoomImg)').click(function() {
                $('.zoomImg').attr('src', $(this).attr('src')).css({width: '100%'});
                $('.zoomDiv').css({opacity: '1', width: 'auto', border: '1px solid white', borderRadius: '5px', position: 'fixed', top: '50%', left: '50%', marginRight: '-50%', transform: 'translate(-50%, -50%)', boxShadow: '0px 0px 50px #888888', zIndex: '50', overflow: 'auto', maxHeight: '100%'});
              });
              // onClick function for zoomImg
              $('img.zoomImg').click(function() {
                $('.zoomDiv').css({opacity: '0', width: '0%'}); 
              });
            });
          </script>
    toc: true
    toc-location: left
    toc-expand: 3
    number-sections: true
    number-depth: 3
    theme: cosmo
    df-print: paged
    code-fold: true 
    output-fold: true
editor: visual
---

First, we will organize the information in our data frame according to the accumulated recommendations for each treatment to observe differences between them. We will focus on the recommendations for each **crop (Rice and Banana)**.

-   Organize our dataset according to the following recommendations:
    -   Accumulated recommendations for each treatment.
    -   Different treatments for each crop, focusing on the principal elements **(N, P, and K)**, recommendations along all farms.
    -   Establish differences between the elements applications.

Through this we will be able to answer the followed questions:

-   How do the different treatments affect the nutrient recommendations for each crop?
-   What are the differences between the nutrient recommendations for each crop?
-   Are we reaching the objectives of the fertilization plan?

let's start by loading the necessary libraries and the data frame.

```{r}
#| echo: true
#| output: false
#| warning: false
#| message: false

# Load the necessary libraries

list_p <- c("tidyverse", "readxl", "soiltexture", 
            "readr", "caret", "plotly", "ggsignif", 
            "reactable")

sapply(list_p, function(x) {
       if(!require(x, character.only = TRUE)) {
         install.packages(x, dependencies = TRUE)
         library(x, character.only = TRUE)
       }
       })

FR_Plan <- read_excel("D:\\OneDrive - CGIAR\\Fertilize Right ADMIN\\ACTIVIDADES\\A3. LB Suelos\\Analisis/Fertilizacion.xlsx", 
                    na = c("null", NA), sheet = "Fertilizations") ## Fertilization plan for both crops
FR_SL <- read_excel("D:\\OneDrive - CGIAR\\Fertilize Right ADMIN\\ACTIVIDADES\\A3. LB Suelos\\Analisis\\Suelos_LB.xlsx",
                    na = c("null", NA), sheet = "Soil charactheristics") ## Soil data analysis results for both crops


str(FR_Plan)
summary(FR_Plan)
```

Once we have our data uploaded, we will focus on the followed variables for our analysis: **Treatment, Crop, and the Nutrient recommendations (N, P, and K)**.

::: {.panel-tabset .nav-pills}
## Rice

```{r}
#| echo: true
#| output: true
#| message: false
#| warning: false

# Observe the difference between N, P, and K applications for the rice crop.

FR_Plan |>
  filter(Cultivo == "Arroz") |>
  group_by(Finca, Tratamiento) |>
  summarize(N = sum(`Aporte N (Kg/ha)`, na.rm = TRUE),
            P = sum(`Aporte P (Kg/ha)`, na.rm = TRUE),
            K = sum(`Aporte K (Kg/ha)`, na.rm = TRUE),
            .groups = "drop") |>
  group_by(Tratamiento) |>
  # Calculate the mean and standard deviation for each nutrient according to each treatment and farm application
  summarize(N_mean = mean(N, na.rm = TRUE),
            P_mean = mean(P, na.rm = TRUE),
            K_mean = mean(K, na.rm = TRUE),
            N_sd = sd(N, na.rm = TRUE),
            P_sd = sd(P, na.rm = TRUE),
            K_sd = sd(K, na.rm = TRUE),
            .groups = "drop") |>
  mutate(Tratamiento = case_when(
    Tratamiento == "Convencional" ~ "Conventional", 
    Tratamiento == "Optimizado" ~ "Optimized", 
    Tratamiento == "Alternativo" ~ "Alternative",
    TRUE ~ Tratamiento)) |>
    pivot_longer(
    cols = -Tratamiento,
    names_to = c("Variable", ".value"),
    names_sep = "_") |>
    mutate(Tratamiento = factor(Tratamiento, 
                              levels = c("Conventional", "Optimized", "Alternative")),
         Variable = factor(Variable, levels = c("N", "P", "K"))) |>
  ggplot(aes(x = Tratamiento, y = mean, 
             fill = Tratamiento)) +
  geom_bar(stat = "identity", position = "dodge", 
           width =  0.65, alpha = 0.65) +
  geom_errorbar(aes(x = Tratamiento, ymin = mean - sd, ymax = mean + sd), 
                width = 0.2, position = position_dodge(0.5), alpha = 0.65) +
facet_wrap(~ Variable, 
           labeller = labeller(Variable = c(N = "N",
                                            P = "P2O5",
                                            K = "K2O")), 
           scales = "free_y") +
  labs(y = expression("Kg/ha")) +
  scale_fill_manual(values = c("#F4A460", "#48D1CC", "#B0E0E6")) +
  guides(color = "none") +
  theme_light(base_size = 12) +
  coord_cartesian(ylim = c(0, 220)) +
  theme(legend.position = "none",
        axis.title.x = element_text(size = 8, face = "bold.italic"),
        axis.title.y = element_text(size = 8, face = "bold.italic"),
        legend.title = element_text(size = 8, face = "bold"),
        axis.text.x = element_text(size = 8, face = "bold", angle = 45, hjust = 1),
        strip.text = element_text(size = 8, face = "bold"))

```

```{r}
#| echo: false
#| output: true
#| warning: false
#| message: false

library(htmltools)
library(fontawesome)

reactable_id <- "fert-download-table"

browsable(
    tagList(
    tags$div(
      style = "margin-bottom: 10px; text-align: center;",
      tags$button(
        tagList(fontawesome::fa("download"), "Download as CSV"),
        onclick = glue::glue("Reactable.downloadDataCSV('{reactable_id}', 'CRS_data.csv')"),
        style = "background-color: #4CAF50; color: white; border: none; padding: 8px 16px; font-size: 14px; cursor: pointer;"
      )
    ),
div(
  style = "display: flex; justify-content: center; width: 100%;",
reactable(
FR_Plan |>
  filter(Cultivo == "Arroz") |>
  group_by(Finca, Tratamiento) |>
  summarize(N = sum(`Aporte N (Kg/ha)`, na.rm = TRUE),
            P = sum(`Aporte P (Kg/ha)`, na.rm = TRUE),
            K = sum(`Aporte K (Kg/ha)`, na.rm = TRUE),
            .groups = "drop") |>
  mutate(Tratamiento = case_when(
    Tratamiento == "Convencional" ~ "Conventional", 
    Tratamiento == "Optimizado" ~ "Optimized", 
    Tratamiento == "Alternativo" ~ "Alternative",
    TRUE ~ Tratamiento)) |>
  group_by(Tratamiento) |>
  # Calculate the mean and standard deviation for each nutrient according to each treatment and farm application
  summarize(N_mean = round(mean(N, na.rm = TRUE),2),
            P_mean = round(mean(P, na.rm = TRUE),2),
            K_mean = round(mean(K, na.rm = TRUE),2),
            # N_sd = round(sd(N, na.rm = TRUE),2),
            # P_sd = round(sd(P, na.rm = TRUE),2),
            # K_sd = round(sd(K, na.rm = TRUE),2),
            .groups = "drop") |>
    pivot_longer(
    cols = -Tratamiento,
    names_to = c("Variable", ".value"),
    names_sep = "_") |>
    mutate(Tratamiento = factor(Tratamiento,
                              levels = c("Conventional", "Optimized", "Alternative")),
         Variable = case_when(Variable == "P" ~ "P2O5",
                              Variable == "K" ~ "K2O",
                              TRUE ~ Variable)) |> 
    set_names(c("Tratamiento", "Variable", "Kg/ha")),
    elementId = reactable_id,
    # Organizing the table to show bellow the graph
    fullWidth = FALSE,
    width = "500px",
    defaultColDef = colDef(cell = function(value) {
                                  format(value, nsmall = 1)
                                  }, 
                    align = 'center', 
                    minWidth = 70,
                    headerStyle = list(background = '#C1CDCD')),
    theme = reactableTheme(
    style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif", 
                 fontSize = 12)),
    bordered = TRUE, 
    highlight = TRUE,
    columns = list("Kg/ha" = colDef(filterable = FALSE)),
    filterable = TRUE
))))

```

## Banana

```{r}
#| echo: true
#| output: true
#| message: false
#| warning: false

FR_Plan |>
  filter(Cultivo == "Banano") |>
  group_by(Finca, Tratamiento, Estado) |>
  summarize(N = sum(`Aporte N (Kg/ha)`, na.rm = TRUE),
            P = sum(`Aporte P (Kg/ha)`, na.rm = TRUE),
            K = sum(`Aporte K (Kg/ha)`, na.rm = TRUE),
            .groups = "drop") |>
  group_by(Tratamiento, Estado) |>
  # Calculate the mean and standard deviation for each nutrient according to each treatment and farm application
  summarize(N_mean = mean(N, na.rm = TRUE),
            P_mean = mean(P, na.rm = TRUE),
            K_mean = mean(K, na.rm = TRUE),
            .groups = "drop") |>
  mutate(Tratamiento = case_when(
    Tratamiento == "Convencional" ~ "Conventional", 
    Tratamiento == "Optimizado" ~ "Optimized", 
    Tratamiento == "Alternativo" ~ "Alternative",
    TRUE ~ Tratamiento)) |>
    pivot_longer(
    cols = -c(Tratamiento, Estado),
    names_to = c("Variable", ".value"),
    names_sep = "_") |>
    mutate(Tratamiento = factor(Tratamiento, 
                              levels = c("Conventional", "Optimized", "Alternative")),
           Variable = factor(Variable, levels = c("N", "P", "K")), 
           Estado = factor(Estado, levels = c("Pendiente", "Aplicado"))) |>
  na.omit() |>
  ggplot(aes(x = Tratamiento, y = mean, 
             fill = Estado)) +
  geom_bar(stat = "identity", 
           width =  0.65, alpha = 0.65) +
  facet_wrap(~ Variable, 
             labeller = labeller(Variable = c(N = "N",
                                            P = "P2O5",
                                            K = "K2O")), 
             scales = "free_y") +
  labs(y = expression("Kg/ha")) +
  scale_fill_manual(values = c("#F4A460", "#48D1CC")) +
  guides(color = "none") +
  theme_light(base_size = 12) +
  coord_cartesian(ylim = c(0, 1000)) +
  theme(axis.title.x = element_text(size = 8, face = "bold.italic"),
        axis.title.y = element_text(size = 8, face = "bold.italic"),
        legend.title = element_text(size = 8, face = "bold"),
        axis.text.x = element_text(size = 8, face = "bold", angle = 45, hjust = 1),
        strip.text = element_text(size = 8, face = "bold"))

```

```{r}
#| echo: false
#| output: true
#| warning: false
#| message: false

reactable_id2 <- "fert-download-table"

browsable(
    tagList(
    tags$div(
      style = "margin-bottom: 10px; text-align: center;",
      tags$button(
        tagList(fontawesome::fa("download"), "Download as CSV"),
        onclick = glue::glue("Reactable.downloadDataCSV('{reactable_id2}', 'CRS_data.csv')"),
        style = "background-color: #4CAF50; color: white; border: none; padding: 8px 16px; font-size: 14px; cursor: pointer;"
      )
    ),
div(
  style = "display: flex; justify-content: center; width: 100%;",
reactable(
FR_Plan |>
  filter(Cultivo == "Banano") |>
  group_by(Finca, Tratamiento) |>
  summarize(N = sum(`Aporte N (Kg/ha)`, na.rm = TRUE),
            P = sum(`Aporte P (Kg/ha)`, na.rm = TRUE),
            K = sum(`Aporte K (Kg/ha)`, na.rm = TRUE),
            .groups = "drop") |>
  group_by(Tratamiento) |>
  # Calculate the mean and standard deviation for each nutrient according to each treatment and farm application
  summarize(N_mean = round(mean(N, na.rm = TRUE),2),
            P_mean = round(mean(P, na.rm = TRUE),2),
            K_mean = round(mean(K, na.rm = TRUE),2),
            .groups = "drop") |>
    pivot_longer(
    cols = -Tratamiento,
    names_to = c("Variable", ".value"),
    names_sep = "_") |>
    mutate(Tratamiento = factor(Tratamiento,
                              levels = c("Convencional", "Optimizado", "Alternativo")),
         Variable = case_when(Variable == "N" ~ "N",
                              Variable == "P" ~ "P2O5",
                              Variable == "K" ~ "K2O",
                              TRUE ~ Variable)) |> 
    set_names(c("Tratamiento", "Variable", "Kg/ha")),
    # Organizing the table to show bellow the graph
    elementId = reactable_id2,
    fullWidth = FALSE,
    width = "400px",
    defaultColDef = colDef(cell = function(value) {
                                  format(value, nsmall = 1)
                                  }, 
                    align = 'center', 
                    minWidth = 70,
                    headerStyle = list(background = '#C1CDCD')),
    theme = reactableTheme(
    style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif", 
                 fontSize = 12)),
    bordered = TRUE, 
    highlight = TRUE,
    columns = list(mean = colDef(filterable = FALSE), 
                  filterable = TRUE)))))

```
:::

Once we have this information, let's calculate the relationship between the applied nitrogen and the available soil. For this process, we will need to organize a table containing the available nitrogen in the soil and the total applied to it to understand the relationship between them and the fulfillment of the requirements of the varieties implemented.

```{r}
#| echo: false
#| output: false
#| warning: false
#| message: false

# calculation of total nitrogen available in soil

N_ava <- FR_SL |>
         rename(Tratamiento = Trat,
                Cultivo = Crop, 
                Finca = Farm, 
                `N Ava (kg/ha)` = "NAva") |>
         mutate(Tratamiento = case_when(
                Tratamiento == "Alternative" ~ "Alternativo", 
                Tratamiento == "Conventional" ~ "Convencional", 
                Tratamiento == "Optimized" ~ "Optimizado",
                TRUE ~ Tratamiento), 
                Cultivo = case_when(
                Cultivo == "Banana" ~ "Banano", 
                Cultivo == "Rice" ~ "Arroz", 
                TRUE ~ Cultivo
                )) |>
         relocate(Tratamiento, .before = Cultivo) |>
         group_by(Finca, Cultivo, Tratamiento, Depth) |>
         summarize(`N Ava (kg/ha)` = round(mean(`N Ava (kg/ha)`), 2),
                  .groups = "drop") |>
         group_by(Finca, Cultivo, Tratamiento) |>
         summarize(`N Ava (kg/ha)` = sum(`N Ava (kg/ha)`, na.rm = TRUE),
                  .groups = "drop") |>
         right_join(FR_Plan, by = c("Finca", "Cultivo", "Tratamiento")) # |>
         # select(Finca, Cultivo, Tratamiento, Product, `N Ava (kg/ha)`, `Aporte N (Kg/ha)`)
# 
# N_ava |> 
#      filter(Cultivo == "Arroz") |>
#      mutate(Var_req  = case_when(
#      Finca == "Farm_1" ~ 189,
#      Finca == "Farm_2" ~ 189,
#      TRUE ~ 166.50)) |> 
#      group_by(Finca, Tratamiento) |>
#      summarize(Napl = sum(`Aporte N (Kg/ha)`, na.rm = TRUE),
#                Navl = mean(`N Ava (kg/ha)`, na.rm = TRUE),
#                Nreq = mean(Var_req, na.rm = TRUE),
#                .groups = "drop") |>
#      mutate(across(c(Napl, Navl), ~ . / Nreq * 100, .names = "{.col}_P")) |>
#      pivot_longer(cols = c(Napl_P, Navl_P), 
#                   names_to = c("Variable", ".value"),
#                   names_sep = "_") |>
#      mutate(Tratamiento = factor(Tratamiento, 
#                                 levels = c("Convencional", "Optimizado", "Alternativo")),
#             Tratamiento = recode(Tratamiento, 
#                                  "Convencional" = "Con",
#                                  "Optimizado" = "Opt",
#                                  "Alternativo" = "Alt"),
#             Finca = factor(Finca, levels =c("Farm_1", "Farm_2", "Farm_3")),
#             Variable = factor(Variable, levels = c("Navl", "Napl"))) |> 
#     # group_by(Tratamiento, Nreq, Variable) |>
#     # summarize(P = mean(P, na.rm = TRUE), .groups = "drop") |>
#      ggplot(aes(x = Tratamiento, y = P)) + 
#      geom_bar(aes(fill = Variable), 
#               stat = "identity", 
#               width = 0.65, alpha = 0.65) + 
#      geom_hline(yintercept = 100, linetype = "dashed", color = "#CD4F39") +
#      facet_wrap(~ Finca, scales = "free_y") +
#      labs(y = expression("%")) +
#      scale_fill_manual(values = c("#48D1CC", "#CD4F39")) +
#      guides(color = "none") +
#      theme_light(base_size = 12) +
#      coord_cartesian(ylim = c(0, 120)) +
#      theme(axis.title.x = element_text(size = 8, face = "bold.italic"),
#         axis.title.y = element_text(size = 8, face = "bold.italic"),
#         legend.title = element_text(size = 8, face = "bold"),
#         axis.text.x = element_text(size = 6, face = "bold"),
#         strip.text = element_text(size = 8, face = "bold"))

```

Let's organize the dataset for each crop according to the requirements of the varieties implemented.

::: {.panel-tabset .nav-pills}
## Rice

```{r}
#| echo: false
#| output: true
#| message: false
#| warning: false

## Barplot with available and applied to the soil percentage

Plot_1 <- suppressWarnings(FR_Plan |> 
     filter(Cultivo == "Arroz") |>
     group_by(Finca, Tratamiento, Product) |>
     summarize("N_kg/ha" = sum(`Aporte N (Kg/ha)`, na.rm = TRUE),
            .groups = "drop") |>
    mutate(Tratamiento = case_when(
           Tratamiento == "Convencional" ~ "Conventional", 
           Tratamiento == "Optimizado" ~ "Optimized", 
           Tratamiento == "Alternativo" ~ "Alternative",
    TRUE ~ Tratamiento)) |>
    group_by(Tratamiento, Product) |>
    summarize(`N_kg/ha` = mean(`N_kg/ha`, na.rm = TRUE),
              .groups = "drop") |>
    pivot_longer(
    cols = -c(Tratamiento, Product),
    names_to = c("Variable", ".value"),
    names_sep = "_") |>
    filter(`kg/ha` > 0) |>
    na.omit() |>
    mutate(Tratamiento = factor(Tratamiento, 
                              levels = c("Conventional", "Optimized", "Alternative"))) |>
     ggplot(aes(x = Tratamiento, y = `kg/ha`)) + 
     geom_bar(aes(fill = Product), 
              stat = "identity", 
              width = 0.65, alpha = 0.65) + 
     scale_fill_manual(values = c("#BCEE68", "#5F9EA0", "#009ACD", 
                                  "#FFB90F", "#FF8C00", "#D1EEEE")) +
     guides(color = "none") +
     theme_light(base_size = 12) +
     coord_cartesian(ylim = c(0, 200)) + 
     xlab("Treatment") +
     theme(axis.title.x = element_text(size = 8, face = "bold.italic"),
        axis.title.y = element_text(size = 8, face = "bold.italic"),
        legend.title = element_text(size = 8, face = "bold"),
        legend.text = element_text(size = 8), 
        axis.text.x = element_text(size = 8, face = "bold", angle = 45, hjust = 1),
        strip.text = element_text(size = 8, face = "bold")))

Plot_2 <- suppressWarnings(FR_Plan |> 
     filter(Cultivo == "Arroz") |>
     mutate(`N Fertilization type`  = case_when(
     Product == "SAM" ~ "Traditional",
     Product == "Triple 18" ~ "Traditional",
     Product == "Urea" ~ "Traditional",
     Product == "Nitroxtend XP-S" ~ "Enhanced urea", 
     Product == "Microessentials" ~ "Traditional",
     Product == "Volcano" ~ "Enhanced urea",
     TRUE ~ Product)) |>
     mutate(Tratamiento = case_when(
           Tratamiento == "Convencional" ~ "Conventional", 
           Tratamiento == "Optimizado" ~ "Optimized", 
           Tratamiento == "Alternativo" ~ "Alternative",
           TRUE ~ Tratamiento)) |>
     group_by(Finca, Tratamiento, Product, `N Fertilization type`) |>
    summarize("N_kg/ha" = sum(`Aporte N (Kg/ha)`, na.rm = TRUE),
            .groups = "drop") |>
    group_by(Tratamiento, Product,`N Fertilization type`) |>
    summarize(`N_kg/ha` = mean(`N_kg/ha`, na.rm = TRUE),
              .groups = "drop") |>
    pivot_longer(
    cols = -c(Tratamiento, `N Fertilization type`),
    names_to = c("Variable", ".value"),
    names_sep = "_") |>
    filter(`kg/ha` > 0) |>
    na.omit() |>
    mutate(Tratamiento = factor(Tratamiento, 
                              levels = c("Conventional", "Optimized", "Alternative")),
           `N Fertilization type` = factor(`N Fertilization type`, 
                                           levels = c("Traditional", "Others", "Enhanced urea"))) |>
     ggplot(aes(x = Tratamiento, y = `kg/ha`)) + 
     geom_bar(aes(fill = `N Fertilization type`), 
              stat = "identity", 
              width = 0.65, alpha = 0.65) + 
     scale_fill_manual(values = c("#48D1CC", "#CD4F39")) +
     guides(color = "none") +
     theme_light(base_size = 12) +
     coord_cartesian(ylim = c(0, 200)) + 
     xlab("Treatment") +
     theme(axis.title.x = element_text(size = 8, face = "bold.italic"),
        axis.title.y = element_text(size = 8, face = "bold.italic"),
        legend.title = element_text(size = 8, face = "bold"),
        legend.text = element_text(size = 8), 
        axis.text.x = element_text(size = 8, face = "bold", angle = 45, hjust = 1),
        strip.text = element_text(size = 8, face = "bold"))) 

gridExtra::grid.arrange(Plot_1, Plot_2, nrow = 1)

```

```{r}
#| echo: false
#| output: false
#| warning: false
#| message: false

suppressWarnings(
  div(
  style = "display: flex; justify-content: center; width: 100%;",
reactable(
 FR_Plan |> 
     filter(Cultivo == "Arroz") |>
     mutate(`Fertilization type`  = case_when(
            Product == "SAM" ~ "Convencional",
            Product == "Triple 18" ~ "Convencional",
            Product == "Urea" ~ "Convencional",
            Product == "Nitroxtend XP-S" ~ "Mejoradas", 
            Product == "Microessentials" ~ "Mejoradas",
     TRUE ~ Product)) |>
     mutate(Tratamiento = case_when(
            Tratamiento == "Convencional" ~ "Conventional", 
            Tratamiento == "Optimizado" ~ "Optimized", 
            Tratamiento == "Alternativo" ~ "Alternative",
            TRUE ~ Tratamiento)) |>
     group_by(Finca, Tratamiento, Product, `Fertilization type`) |>
     summarize("N_kg/ha" = mean(`Aporte N (Kg/ha)`, na.rm = TRUE),
            .groups = "drop") |> 
    pivot_longer(
    cols = -c(Tratamiento, Product, `Fertilization type`),
    names_to = c("Variable", ".value"),
    names_sep = "_") |>
    filter(`kg/ha` > 0) |>
    na.omit() |>
    mutate(Tratamiento = factor(Tratamiento, 
                              levels = c("Conventional", "Optimized", "Alternative"))),
# Organizing the table to show bellow the graph
    fullWidth = FALSE,
    width = "400px",
    defaultColDef = colDef(cell = function(value) {
                                  format(value, nsmall = 1)
                                  }, 
                    align = 'center', 
                    minWidth = 70,
                    headerStyle = list(background = '#C1CDCD')),
    theme = reactableTheme(
    style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif", 
                 fontSize = 12)),
    bordered = TRUE, 
    highlight = TRUE,
    columns = list(Nreq = colDef(filterable = FALSE), 
                   P = colDef(filterable = FALSE)),
    filterable = TRUE
)))

```

```{r}
#| echo: false
#| output: true
#| warning: false
#| message: false

# Lets define the table according the NH4 and No3 levels, also we must include the total of nitrogen  applied

suppressWarnings(
  div(
  style = "display: flex; justify-content: center; width: 100%;",
reactable(
 FR_Plan |> 
     filter(Cultivo == "Arroz") |>
     mutate(Tratamiento = case_when(
            Tratamiento == "Convencional" ~ "Conventional", 
            Tratamiento == "Optimizado" ~ "Optimized", 
            Tratamiento == "Alternativo" ~ "Alternative",
            TRUE ~ Tratamiento)) |>
    group_by(Finca, Tratamiento) |>
    summarize("NO3 (kg/ha)" = sum(`Aporte NO3 (kg/ha)`, na.rm = TRUE),
              "NH4 (kg/ha)" = sum(`Aporte NH4 (kg/ha)`, na.rm = TRUE),
              "N Total (kg/ha)" = sum(`Aporte N (Kg/ha)`, na.rm = TRUE),
              .groups = "drop") |>
    group_by(Tratamiento) |>
    summarize(`NO3 (kg/ha)` = mean(`NO3 (kg/ha)`, na.rm = TRUE),
              `NH4 (kg/ha)` = mean(`NH4 (kg/ha)`, na.rm = TRUE),
              `N Total (kg/ha)` = mean(`N Total (kg/ha)`, na.rm = TRUE),
              .groups = "drop") |> 
    mutate(Tratamiento = factor(Tratamiento, 
                              levels = c("Conventional", "Optimized", "Alternative"))) |> 
    arrange(Tratamiento) |> 
    rename(Treatment = "Tratamiento"),
# Organizing the table to show bellow the graph
    fullWidth = FALSE,
    width = "400px",
    defaultColDef = colDef(cell = function(value) {
                                  format(value, nsmall = 1)
                                  }, 
                    align = 'center', 
                    minWidth = 70,
                    headerStyle = list(background = '#C1CDCD')),
    theme = reactableTheme(
    style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif", 
                 fontSize = 12)),
    bordered = TRUE, 
    highlight = TRUE,
    columns = list(Nreq = colDef(filterable = FALSE), 
                   P = colDef(filterable = FALSE)),
    filterable = TRUE
)))

```

```{r}
#| echo: false
#| output: false
#| message: false
#| warning: false
#| fig-height: 2

# Define a function to generate the pie chart for each farm
# generate_pie <- function(farm) {
#   N_ava |>
#      filter(Cultivo == "Arroz", Finca == farm) |>
#      mutate(Var_req  = case_when(
#      Finca == "Farm_1" ~ 189,
#      Finca == "Farm_2" ~ 189,
#      TRUE ~ 166.50)) |>
#      group_by(Finca, Tratamiento) |>
#      summarize(Napl = sum(`Aporte N (Kg/ha)`, na.rm = TRUE),
#                Navl = mean(`N Ava (kg/ha)`, na.rm = TRUE),
#                Nreq = mean(Var_req, na.rm = TRUE),
#                .groups = "drop") |>
#      mutate(across(c(Napl, Navl), ~ . / Nreq * 100, .names = "{.col}_P")) |>
#      pivot_longer(cols = c(Napl_P, Navl_P),
#                   names_to = c("Variable", ".value"),
#                   names_sep = "_") |>
#      mutate(Tratamiento = factor(Tratamiento,
#                                 levels = c("Convencional", "Optimizado", "Alternativo")),
#             Tratamiento = recode(Tratamiento,
#                                  "Convencional" = "Con",
#                                  "Optimizado" = "Opt",
#                                  "Alternativo" = "Alt"),
#             Finca = factor(Finca, levels =c("Farm_1", "Farm_2", "Farm_3")),
#             Variable = factor(Variable, levels = c("Navl", "Napl")),
#             P = round(P, 2)) |>
#      ggplot(aes(x = "", y = P)) +
#      geom_bar(aes(fill = Variable),
#               stat = "identity",
#               width = 0.65, alpha = 0.65) +
#      coord_polar(theta = "y", start=0) +
#      facet_wrap(~ Tratamiento, scales = "free_y") +
#      labs(title = paste("Nitrogen % -", farm)) +
#      scale_fill_manual(values = c("#48D1CC", "#CD4F39")) +
#      guides(color = "none") +
#      theme_classic(base_size = 12) +
#      theme(axis.title.x = element_blank(),
#         axis.title.y = element_blank(),
#         legend.title = element_text(size = 8, face = "bold"),
#         axis.text.x = element_blank(),
#         axis.text.y = element_blank(),
#         strip.text = element_text(size = 8, face = "bold"),
#         axis.line=element_blank(),
#         axis.ticks = element_blank()) +
#      geom_text(aes(
#      label=paste0(P,"%")),
#      position=position_stack(vjust=0.5),
#      size=3)
# }
# 
# # Generate plots for each farm
# pie_farm1 <- generate_pie("Farm_1")
# pie_farm2 <- generate_pie("Farm_2")
# pie_farm3 <- generate_pie("Farm_3")
# 
# pie_farm1
# pie_farm2
# pie_farm3

```

## Banana

```{r, warning=FALSE}
#| echo: true
#| output: true
#| message: false
#| warning: false


suppressWarnings(FR_Plan |> 
     filter(Cultivo == "Banano") |>
     group_by(Finca, Tratamiento, Product) |>
     summarize("N_kg/ha" = sum(`Aporte N (Kg/ha)`, na.rm = TRUE),
            .groups = "drop") |>
    group_by(Tratamiento, Product) |>
    summarize(`N_kg/ha` = mean(`N_kg/ha`, na.rm = TRUE),
              .groups = "drop") |>
    pivot_longer(
    cols = -c(Tratamiento, Product),
    names_to = c("Variable", ".value"),
    names_sep = "_") |>
    filter(`kg/ha` > 0) |>
    na.omit() |>
    mutate(Tratamiento = factor(Tratamiento, 
                              levels = c("Convencional", "Optimizado", "Alternativo"))) |>
     ggplot(aes(x = Tratamiento, y = `kg/ha`)) + 
     geom_bar(aes(fill = Product), 
              stat = "identity", 
              width = 0.40, alpha = 0.65) + 
     scale_fill_manual(values = c("#BCEE68", "#5F9EA0", "#009ACD", 
                                  "#FFB90F", "#FF8C00", "#EE6363", 
                                  "#EEE685", "#CD69C9", "#EECBAD", 
                                  "#CD0000", "#3A5FCD", "#708090")) +
     xlab("Treatment") +
     guides(color = "none") +
     theme_light(base_size = 12) +
     # coord_cartesian(ylim = c(0, 350)) + 
     theme(axis.title.x = element_text(size = 8, face = "bold.italic"),
        axis.title.y = element_text(size = 8, face = "bold.italic"),
        legend.title = element_text(size = 8, face = "bold"),
        axis.text.x = element_text(size = 8, face = "bold", angle = 45, hjust = 1),
        strip.text = element_text(size = 8, face = "bold")))

```

```{r}
#| echo: false
#| output: true
#| warning: false
#| message: false

suppressWarnings(
  div(
  style = "display: flex; justify-content: center; width: 100%;",

reactable(
 FR_Plan |> 
     filter(Cultivo == "Banano") |>
     mutate(Tratamiento = case_when(
            Tratamiento == "Convencional" ~ "Conventional", 
            Tratamiento == "Optimizado" ~ "Optimized", 
            Tratamiento == "Alternativo" ~ "Alternative",
            TRUE ~ Tratamiento)) |>
    group_by(Finca, Tratamiento) |>
    summarize("NO3 (kg/ha)" = sum(`Aporte NO3 (kg/ha)`, na.rm = TRUE),
              "NH4 (kg/ha)" = sum(`Aporte NH4 (kg/ha)`, na.rm = TRUE),
              "N Total (kg/ha)" = sum(`Aporte N (Kg/ha)`, na.rm = TRUE),
              .groups = "drop") |>
    group_by(Tratamiento) |>
    summarize(`NO3 (kg/ha)` = mean(`NO3 (kg/ha)`, na.rm = TRUE),
              `NH4 (kg/ha)` = mean(`NH4 (kg/ha)`, na.rm = TRUE),
              `N Total (kg/ha)` = mean(`N Total (kg/ha)`, na.rm = TRUE),
              .groups = "drop") |> 
    mutate(Tratamiento = factor(Tratamiento, 
                              levels = c("Conventional", "Optimized", "Alternative"))) |> 
    arrange(Tratamiento) |> 
    rename(Treatment = "Tratamiento"),
# Organizing the table to show bellow the graph
    fullWidth = FALSE,
    width = "400px",
    defaultColDef = colDef(cell = function(value) {
                                  format(value, nsmall = 1)
                                  }, 
                    align = 'center', 
                    minWidth = 70,
                    headerStyle = list(background = '#C1CDCD')),
    theme = reactableTheme(
    style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif", 
                 fontSize = 12)),
    bordered = TRUE, 
    highlight = TRUE,
    columns = list(Nreq = colDef(filterable = FALSE), 
                   P = colDef(filterable = FALSE)),
    filterable = TRUE
)))

```

```{r}
#| echo: false
#| output: false
#| message: false
#| warning: false
#| fig-height: 2

# # Define a function to generate the pie chart for each farm
# generate_pie <- function(farm) {
#   N_ava |> 
#      filter(Cultivo == "Banano", Finca == farm) |>
#      mutate(Var_req  = case_when(
#      Finca == "Farm_1" ~ 321,
#      Finca == "Farm_2" ~ 321,
#      TRUE ~ 321)) |> 
#      group_by(Finca, Tratamiento) |>
#      summarize(Napl = sum(`Aporte N (Kg/ha)`, na.rm = TRUE),
#                Navl = mean(`N Ava (kg/ha)`, na.rm = TRUE),
#                Nreq = mean(Var_req, na.rm = TRUE),
#                .groups = "drop") |>
#      mutate(across(c(Napl, Navl), ~ . / Nreq * 100, .names = "{.col}_P")) |>
#      pivot_longer(cols = c(Napl_P, Navl_P), 
#                   names_to = c("Variable", ".value"),
#                   names_sep = "_") |>
#      mutate(Tratamiento = factor(Tratamiento, 
#                                 levels = c("Convencional", "Optimizado", "Alternativo")),
#             Tratamiento = recode(Tratamiento, 
#                                  "Convencional" = "Con",
#                                  "Optimizado" = "Opt",
#                                  "Alternativo" = "Alt"),
#             Finca = factor(Finca, levels =c("Farm_1", "Farm_2", "Farm_3")),
#             Variable = factor(Variable, levels = c("Navl", "Napl")), 
#             P = round(P, 2)) |> 
#      ggplot(aes(x = "", y = P)) + 
#      geom_bar(aes(fill = Variable), 
#               stat = "identity", 
#               width = 0.65, alpha = 0.65) + 
#      coord_polar(theta = "y", start=0) +  
#      facet_wrap(~ Tratamiento, scales = "free_y") +
#      labs(title = paste("Nitrogen % -", farm)) +
#      scale_fill_manual(values = c("#48D1CC", "#CD4F39")) +
#      guides(color = "none") +
#      theme_classic(base_size = 12) +
#      theme(axis.title.x = element_blank(),
#         axis.title.y = element_blank(),
#         legend.title = element_text(size = 8, face = "bold"),
#         axis.text.x = element_blank(),
#         axis.text.y = element_blank(),
#         strip.text = element_text(size = 8, face = "bold"), 
#         axis.line=element_blank(), 
#         axis.ticks = element_blank()) + 
#      geom_text(aes(
#      label=paste0(P,"%")), 
#      position=position_stack(vjust=0.5), 
#      size=3)
# }
# 
# # Generate plots for each farm
# pie_farm1 <- generate_pie("Farm_1")
# pie_farm2 <- generate_pie("Farm_2")
# pie_farm3 <- generate_pie("Farm_3")
# 
# pie_farm1
# pie_farm2
# pie_farm3

```
:::

Now that we have differentiate the nutrient application levels by each crop, lets evaluate the different level of soil fertilizers applications.

::: {.panel-tabset .nav-pills}
## Arroz

```{r}
#| echo: false
#| output: true
#| message: false
#| warning: false

## Disponibilidad acorde requerimiento promedio
N_ava |> 
     filter(Cultivo == "Arroz") |>
     mutate(Var_req  = case_when(
     Finca == "Farm_1" ~ 189,
     Finca == "Farm_2" ~ 189,
     TRUE ~ 166.50)) |>
     mutate(Tratamiento = case_when(
            Tratamiento == "Convencional" ~ "Conventional", 
            Tratamiento == "Optimizado" ~ "Optimized", 
            Tratamiento == "Alternativo" ~ "Alternative",
            TRUE ~ Tratamiento)) |>
     group_by(Finca, Tratamiento) |>
     summarize(Napl = sum(`Aporte N (Kg/ha)`, na.rm = TRUE),
               Navl = mean(`N Ava (kg/ha)`, na.rm = TRUE),
               Nreq = mean(Var_req, na.rm = TRUE),
               .groups = "drop") |>
    filter(Napl > 0) |>
    group_by(Tratamiento) |>
    summarize(Napl = mean(Napl),    # Total sum per Tratamiento
              Navl = sum(Navl),    # Total sum per Tratamiento
              .groups = "drop") |>
    pivot_longer(cols = -c(Tratamiento),
                 names_to = c("Variable"),
                 values_to = "kg/ha") |> 
     mutate(Tratamiento = factor(Tratamiento,
                                levels = c("Conventional", "Optimized", "Alternative")), 
            Variable = factor(Variable, 
                              levels = c("Navl", "Napl"))) |>
     ggplot(aes(x = Tratamiento, y = `kg/ha`)) +
     geom_bar(aes(fill = Variable), stat = "identity",
              width = .45, alpha = 0.65, position = "dodge") +
     geom_hline(yintercept = 170, linetype = "dashed", color = "#CD4F39") +
     scale_fill_manual(name = "Nitrogen", 
                       labels = c("Available", "Applied"),
                       values = c("#FF8C00", "#48D1CC")) +
     xlab("Treatment") +
     guides(color = "none") +
     theme_light(base_size = 12) +
     coord_cartesian(ylim = c(0, 250)) +
    # facet_wrap(~ Finca, scales = "free_y") +
     theme(axis.title.x = element_text(size = 8, face = "bold.italic"),
        axis.title.y = element_text(size = 8, face = "bold.italic"),
        legend.title = element_text(size = 8, face = "bold"),
        axis.text.x = element_text(size = 8, face = "bold", angle = 45, hjust = 1),
        strip.text = element_text(size = 8, face = "bold"))

```

```{r}
#| echo: false
#| output: false
#| message: false
#| warning: false

## Disponibilidad acorde requerimiento promedio
N_ava |> 
     filter(Cultivo == "Arroz") |>
     mutate(Var_req  = case_when(
     Finca == "Farm_1" ~ 189,
     Finca == "Farm_2" ~ 189,
     TRUE ~ 166.50)) |>
     mutate(Tratamiento = case_when(
            Tratamiento == "Convencional" ~ "Conventional", 
            Tratamiento == "Optimizado" ~ "Optimized", 
            Tratamiento == "Alternativo" ~ "Alternative",
            TRUE ~ Tratamiento)) |>
     group_by(Finca, Tratamiento, Product) |>
     summarize(Napl = sum(`Aporte N (Kg/ha)`, na.rm = TRUE),
               Navl = mean(`N Ava (kg/ha)`, na.rm = TRUE),
               Nreq = mean(Var_req, na.rm = TRUE),
               .groups = "drop") |>
    filter(Napl > 0) |>
    mutate(across(c(Napl), ~ . / Nreq * 100, .names = "{.col}_P")) |>
    pivot_longer(cols = c(Napl_P),
                  names_to = c("Variable", ".value"),
                  names_sep = "_") |> 
     mutate(Tratamiento = factor(Tratamiento,
                                levels = c("Conventional", "Optimized", "Alternative")),
            Tratamiento = recode(Tratamiento,
                                 "Convencional" = "Con",
                                 "Optimizado" = "Opt",
                                 "Alternativo" = "Alt"),
            Finca = factor(Finca, levels =c("Farm_1", "Farm_2", "Farm_3"))) |>
     ggplot(aes(x = Tratamiento, y = P)) +
     geom_bar(aes(fill = Product),
              stat = "identity",
              width = 0.65, alpha = 0.65) +
     geom_hline(yintercept = 100, linetype = "dashed", color = "#CD4F39") +
     facet_wrap(~ Finca, scales = "free_y") +
     labs(y = expression("%")) +
     scale_fill_manual(values = c("#48D1CC", "#668B8B", "#009ACD", "#8DB6CD", "#BCD2EE", "#B0C4DE")) +
     guides(color = "none") +
     theme_light(base_size = 12) +
     coord_cartesian(ylim = c(0, 120)) +
     theme(axis.title.x = element_text(size = 8, face = "bold.italic"),
        axis.title.y = element_text(size = 8, face = "bold.italic"),
        legend.title = element_text(size = 8, face = "bold"),
        axis.text.x = element_text(size = 6, face = "bold"),
        strip.text = element_text(size = 8, face = "bold"))

```

```{r}
#| echo: false
#| output: false
#| warning: false
#| message: false

library(reactable)
div(
  style = "display: flex; justify-content: center; width: 100%;",
  
reactable(
N_ava |> 
     filter(Cultivo == "Arroz") |>
     mutate(Var_req  = case_when(
     Finca == "Farm_1" ~ 189,
     Finca == "Farm_2" ~ 189,
     TRUE ~ 166.50)) |>
     group_by(Finca, Tratamiento, Product) |>
     summarize(Napl = sum(`Aporte N (Kg/ha)`, na.rm = TRUE),
               Navl = mean(`N Ava (kg/ha)`, na.rm = TRUE),
               Nreq = mean(Var_req, na.rm = TRUE),
               .groups = "drop") |>
    filter(Napl > 0) |>
    mutate(across(c(Napl), ~ . / Nreq * 100, .names = "{.col}_P")) |>
    pivot_longer(cols = c(Napl_P),
                  names_to = c("Variable", ".value"),
                  names_sep = "_") |> 
     mutate(Tratamiento = factor(Tratamiento,
                                levels = c("Convencional", "Optimizado", "Alternativo")),
            Tratamiento = recode(Tratamiento,
                                 "Convencional" = "Con",
                                 "Optimizado" = "Opt",
                                 "Alternativo" = "Alt"),
            Finca = factor(Finca, levels =c("Farm_1", "Farm_2", "Farm_3"))) |> 
  select(Finca, Tratamiento, Product, P),
# Organizing the table to show bellow the graph
    fullWidth = FALSE,
    width = "400px",
    defaultColDef = colDef(cell = function(value) {
                                  format(value, nsmall = 1)
                                  }, 
                    align = 'center', 
                    minWidth = 70,
                    headerStyle = list(background = '#C1CDCD')),
    theme = reactableTheme(
    style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif", 
                 fontSize = 12)),
    bordered = TRUE, 
    highlight = TRUE,
    columns = list(Nreq = colDef(filterable = FALSE), 
                   P = colDef(filterable = FALSE)),
    filterable = TRUE
))

```

## Banano

```{r}
#| echo: false
#| output: true
#| message: false
#| warning: false

N_ava |> 
     filter(Cultivo == "Banano") |>
     mutate(Var_req  = case_when(
     Finca == "Farm_1" ~ 321,
     Finca == "Farm_2" ~ 321,
     TRUE ~ 321)) |>
     mutate(Tratamiento = case_when(
            Tratamiento == "Convencional" ~ "Conventional", 
            Tratamiento == "Optimizado" ~ "Optimized", 
            Tratamiento == "Alternativo" ~ "Alternative",
            TRUE ~ Tratamiento)) |>
      group_by(Finca, Tratamiento) |>
     summarize(Napl = sum(`Aporte N (Kg/ha)`, na.rm = TRUE),
               Navl = mean(`N Ava (kg/ha)`, na.rm = TRUE),
               Nreq = mean(Var_req, na.rm = TRUE),
               .groups = "drop") |>
    filter(Napl > 0) |>
    group_by(Tratamiento) |>
    summarize(Napl = mean(Napl),    # Total sum per Tratamiento
              Navl = mean(Navl),    # Total sum per Tratamiento
              .groups = "drop") |>
    pivot_longer(cols = -c(Tratamiento),
                 names_to = c("Variable"),
                 values_to = "kg/ha") |> 
     mutate(Tratamiento = factor(Tratamiento,
                                levels = c("Conventional", "Optimized", "Alternative")), 
            Variable = factor(Variable, 
                              levels = c("Navl", "Napl"))) |>
     ggplot(aes(x = Tratamiento, y = `kg/ha`)) +
     geom_bar(aes(fill = Variable),stat = "identity",
              width = 0.45, alpha = 0.65, position = "dodge") +
     geom_hline(yintercept = 321, linetype = "dashed", color = "#CD4F39") +
     scale_fill_manual(name = "Nitrogen", 
                       labels = c("Available", "Applied"),
                       values = c("#FF8C00", "#48D1CC")) +
     xlab("Treatment") +
     guides(color = "none") +
     theme_light(base_size = 12) +
     coord_cartesian(ylim = c(0, 500)) +
     # facet_wrap(~ Finca, scales = "free_y") +
     theme(axis.title.x = element_text(size = 8, face = "bold.italic"),
        axis.title.y = element_text(size = 8, face = "bold.italic"),
        legend.title = element_text(size = 8, face = "bold"),
        axis.text.x = element_text(size = 8, face = "bold", angle = 45, hjust = 1),
        strip.text = element_text(size = 8, face = "bold"))

```

```{r}
#| echo: false
#| output: false
#| warning: false
#| message: false

div(
  style = "display: flex; justify-content: center; width: 100%;",
reactable(
N_ava |> 
     filter(Cultivo == "Banano") |>
     mutate(Var_req  = case_when(
     Finca == "Farm_1" ~ 321,
     Finca == "Farm_2" ~ 321,
     TRUE ~ 321)) |>
     group_by(Finca, Tratamiento, Product) |>
     summarize(Napl = sum(`Aporte N (Kg/ha)`, na.rm = TRUE),
               Navl = mean(`N Ava (kg/ha)`, na.rm = TRUE),
               Nreq = mean(Var_req, na.rm = TRUE),
               .groups = "drop") |>
    filter(Napl > 0) |>
    mutate(across(c(Napl), ~ . / Nreq * 100, .names = "{.col}_P")) |>
    pivot_longer(cols = c(Napl_P),
                  names_to = c("Variable", ".value"),
                  names_sep = "_") |> 
     mutate(Tratamiento = factor(Tratamiento,
                                levels = c("Convencional", "Optimizado", "Alternativo")),
            Tratamiento = recode(Tratamiento,
                                 "Convencional" = "Con",
                                 "Optimizado" = "Opt",
                                 "Alternativo" = "Alt"),
            Finca = factor(Finca, levels =c("Farm_1", "Farm_2", "Farm_3"))) |> 
  select(Finca, Tratamiento, Product, P),
# Organizing the table to show bellow the graph
    fullWidth = FALSE,
    width = "400px",
    defaultColDef = colDef(cell = function(value) {
                                  format(value, nsmall = 1)
                                  }, 
                    align = 'center', 
                    minWidth = 70,
                    headerStyle = list(background = '#C1CDCD')),
    theme = reactableTheme(
    style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif", 
                 fontSize = 12)),
    bordered = TRUE, 
    highlight = TRUE,
    columns = list(Nreq = colDef(filterable = FALSE), 
                   P = colDef(filterable = FALSE)),
    filterable = TRUE
))
```
:::

Let's generate a timeline representing the fertilization dates in each farm and crop.

## Arroz

::: {.panel-tabset .nav-pills}
## Farm 1

```{r}
#| echo: false
#| output: true
#| message: false
#| warning: false

library(png)
library(grid)

Rce_img <- readPNG("D:\\OneDrive - CGIAR\\Fetilize right projects\\Rice\\Images\\Rice growht.png")
bg_g <- rasterGrob(Rce_img, width = unit(1, "npc"), height = unit(1, "npc"))

FR_Plan |>
  filter(Cultivo == "Arroz" & Finca == "Farm_1") |>
   mutate(Activity = factor(Activity),                # make sure Activity is a factor
         y = as.numeric(Activity)) |>
  ggplot(aes(x = DDS, y = y)) +
  annotation_custom(bg_g, xmin = 1, xmax = 10, ymin = -4, ymax = 6) +
  geom_segment(aes(x = DDS, xend = DDS, y = 0, yend = y), 
               linetype = "dotted", color = "deeppink", size = 0.7) +
  geom_point(aes(color = Activity), size = 4) + 
  # geom_vline(aes(xintercept = DDS, color = "red"),
             # linetype = "dotted", size = 0.7, show.legend = FALSE) +
  scale_y_continuous(breaks = NULL) +
    labs(x = "DDS", y = NULL, title = "Fertilization Timeline - Farm_1") +
  theme_minimal(base_size = 12) +
  theme(axis.title = element_text(size = 8, face = "bold.italic"),
        axis.title.x = element_text(size = 8, face = "bold.italic"),
        axis.title.y = element_text(size = 8, face = "bold.italic"),
        legend.title = element_text(size = 8, face = "bold"),
        legend.text = element_text(size = 8), 
        axis.text.x = element_text(size = 8, face = "bold", angle = 45, hjust = 1),
        strip.text = element_text(size = 8, face = "bold"))
```

## Farm 2

```{r}
#| echo: false
#| output: true
#| message: false
#| warning: false

FR_Plan |>
  filter(Cultivo == "Arroz" & Finca == "Farm_2") |>
   mutate(Activity = factor(Activity),                # make sure Activity is a factor
         y = as.numeric(Activity)) |>
  ggplot(aes(x = DDS, y = y)) +
  annotation_custom(bg_g, xmin = 1, xmax = 8, ymin = -3.5, ymax = 5) +
  geom_segment(aes(x = DDS, xend = DDS, y = 0, yend = y), 
               linetype = "dotted", color = "deeppink", size = 0.7) +
  geom_point(aes(color = Activity), size = 4) + 
  # geom_vline(aes(xintercept = DDS, color = "red"),
             # linetype = "dotted", size = 0.7, show.legend = FALSE) +
  scale_y_continuous(breaks = NULL) +
    labs(x = "DDS", y = NULL, title = "Fertilization Timeline - Farm_2") +
  theme_minimal(base_size = 12) +
  theme(axis.title = element_text(size = 8, face = "bold.italic"),
        axis.title.x = element_text(size = 8, face = "bold.italic"),
        axis.title.y = element_text(size = 8, face = "bold.italic"),
        legend.title = element_text(size = 8, face = "bold"),
        legend.text = element_text(size = 8), 
        axis.text.x = element_text(size = 8, face = "bold", angle = 45, hjust = 1),
        strip.text = element_text(size = 8, face = "bold"))
```

## Farm 3

```{r}
#| echo: false
#| output: true
#| message: false
#| warning: false

FR_Plan |>
  filter(Cultivo == "Arroz" & Finca == "Farm_3") |>
   mutate(Activity = factor(Activity),                # make sure Activity is a factor
         y = as.numeric(Activity)) |>
  ggplot(aes(x = DDS, y = y)) +
  annotation_custom(bg_g, xmin = 1, xmax = 10, ymin = -3.5, ymax = 5) +
  geom_segment(aes(x = DDS, xend = DDS, y = 0, yend = y), 
               linetype = "dotted", color = "deeppink", size = 0.7) +
  geom_point(aes(color = Activity), size = 4) + 
  # geom_vline(aes(xintercept = DDS, color = "red"),
             # linetype = "dotted", size = 0.7, show.legend = FALSE) +
  scale_y_continuous(breaks = NULL) +
    labs(x = "DDS", y = NULL, title = "Fertilization Timeline - Farm_3") +
  theme_minimal(base_size = 12) +
  theme(axis.title = element_text(size = 8, face = "bold.italic"),
        axis.title.x = element_text(size = 8, face = "bold.italic"),
        axis.title.y = element_text(size = 8, face = "bold.italic"),
        legend.title = element_text(size = 8, face = "bold"),
        legend.text = element_text(size = 8), 
        axis.text.x = element_text(size = 8, face = "bold", angle = 45, hjust = 1),
        strip.text = element_text(size = 8, face = "bold"))
```
:::